Extracellular potentials generated by axonal projections are shaped by patterns of bifurcations and terminations

### 2016-02-25 doc/manuscript.tex
caption changes

The point of the polarity reversal coincides roughly with the middle of
the projection zone. This means that the absolute value of the response
amplitude reaches a local minimum just when the number of axonal fibers
reaches a maximum. To better understand how anatomical features and
response amplitude are related, we compared the signed maximum value
(meaning the \emph{signed} value corresponding to the maximum
\emph{absolute} amplitude) of the EFP with the difference in the density
of branchings and terminations (Figure 1C). Interestingly, the amplitude
of the maximum response (red trace) follows the distribution of
branchings and terminations (black histogram).

Along the nerve trunk the fiber density is constant, and the amplitude
is unchanged. As the axon bundle reaches its projection zone, the number
of bifurcations increases, and the response increases in amplitude. In
the middle of the projection zone, the number of bifurcations and
terminations cancels out. At the same depth, the amplitude crosses zero.
As the end of the projection zone approaches, the terminations outweigh
the bifurcations, and the amplitude increases, but the polarity is
reversed. This transition also corresponds to the traces in the red box
in Figure 1B. As the axon bundle ends, there are no longer any
bifurcations or terminations, and the amplitude decays toward zero.

>>>>

The point of the polarity reversal coincides roughly with the middle of
the projection zone. This means that the absolute value of the response
amplitude reaches a local minimum just when the number of axonal fibers
reaches a maximum. To better understand how anatomical features and
response amplitude are related, we compared the signed maximum value
(meaning the \emph{signed} value corresponding to the maximum
\emph{absolute} amplitude) of the EFP with the difference in the density
of branchings and terminations (Figure 1C).

Along the nerve trunk the fiber density is constant. As the axon bundle
reaches its projection zone, the number of bifurcations increases. In
the middle of the projection zone, the number of bifurcations and
terminations cancels out. At the same depth, the amplitude crosses zero.
As the end of the projection zone approaches, the terminations outweigh
the bifurcations. As the axon bundle ends, there are no longer any
bifurcations or terminations, and the density decays toward zero.

\begin{itemize}
\tightlist
\item
  Compare B and C
\end{itemize}

Interestingly, the amplitude of the maximum response (red trace) follows
the distribution of branchings and terminations (black histogram).
